GSE158420: RNA expression downsampling

### 2024-09-13 analysis/GSE158420_rna.Rmd
png
ms
nice violin plot for downsampling

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("HGNChelper")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("gplots")
  library("gridExtra")
  library("png")
  library("fgsea")
  library("parallel")
  library("RhpcBLASctl")
  library("tictoc")
  library("edgeR")
})

@@

@@

@@

>>>>

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("HGNChelper")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("gplots")
  library("gridExtra")
  library("png")
  library("fgsea")
  library("parallel")
  library("RhpcBLASctl")
  library("tictoc")
  library("edgeR")
  library("vioplot")
})

@@

This will run the FGSEA analysis at group sizes of 2, 3, 5, 10, 16, 22 and 30,
50 times each, with pseudorandom seeds from 100 to 5000 jumping up by 100.

@@

### PNG
png("fig4.png", width=7,height=5,units="in",res=150,pointsize=12)
par(mfrow=c(1,3))

@@

## Make violin plot

```{r,vioplot}

length(osets)
length(fsets)

names(fores) <- names(fgres) <- as.character(c(2,3,5,10,15,20,25,30))

vioplot(lapply(fores,function(mx) { mx[,2] } ) , side="left" , col="white" , border = "red",
  plotCentre = "line", ylim=c(0,457), xlab="Sample size", ylab="no. pathways")
  mtext("no. consistent pathways FDR<0.05" )
vioplot(lapply(fgres,function(mx) { mx[,2] } ) , side="right" , col="white", border="blue" ,
   add = TRUE, plotCentre = "line")

abline(h=length(osets),col="red")
abline(h=length(fsets),col="blue")

vioplot(lapply(fores,function(mx) { mx[,3] } ) , side="left" , col="white" , border="red",
  plotCentre = "line", ylim=c(0,210), xlab="Sample size", ylab="no. pathways")
  mtext("no. inconsistent pathways FDR<0.05" )
vioplot(lapply(fgres,function(mx) { mx[,3] } ) , side="right" , col="white", border="blue",
  add = TRUE , plotCentre = "line")

fg1 <- lapply(fgres,function(mx) { TP <- mx[,2] ; FP <- mx[,3]  ; FP / (TP + FP) } )
fo1 <- lapply(fores,function(mx) { TP <- mx[,2] ; FP <- mx[,3]  ; FP / (TP + FP) } )

vioplot(fo1 , side="left" , col="white", border="red", plotCentre = "line",
  ylim=c(0,0.5), xlab="Sample size", ylab="no. pathways")
  mtext("proportion inconsistent pathways" )
vioplot(fg1 , side="right" , col="white", border="blue", add = TRUE , plotCentre = "line")

### PDF CHART
pdf("sens_vio.pdf",height=4,width=8)
par(mfrow=c(1,3))
vioplot(lapply(fores,function(mx) { mx[,2] } ) , side="left" , col="white" , border = "red",
  plotCentre = "line", ylim=c(0,457), xlab="Sample size", ylab="no. pathways")
  mtext("no. consistent pathways FDR<0.05" ,cex=0.8)
vioplot(lapply(fgres,function(mx) { mx[,2] } ) , side="right" , col="white", border="blue" ,
   add = TRUE, plotCentre = "line")

abline(h=length(osets),col="red")
abline(h=length(fsets),col="blue")

vioplot(lapply(fores,function(mx) { mx[,3] } ) , side="left" , col="white" , border="red",
  plotCentre = "line", ylim=c(0,210), xlab="Sample size", ylab="no. pathways")
  mtext("no. inconsistent pathways FDR<0.05" , cex=0.8)
vioplot(lapply(fgres,function(mx) { mx[,3] } ) , side="right" , col="white", border="blue",
  add = TRUE , plotCentre = "line")

fg1 <- lapply(fgres,function(mx) { TP <- mx[,2] ; FP <- mx[,3]  ; FP / (TP + FP) } )
fo1 <- lapply(fores,function(mx) { TP <- mx[,2] ; FP <- mx[,3]  ; FP / (TP + FP) } )

vioplot(fo1 , side="left" , col="white", border="red", plotCentre = "line",
  ylim=c(0,0.5), xlab="Sample size", ylab="no. pathways")
  mtext("proportion inconsistent pathways",, cex=0.8)
vioplot(fg1 , side="right" , col="white", border="blue", add = TRUE , plotCentre = "line")
dev.off()
